A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-08-26 rr-flow.Rmd
add automated wordcount closes #16
take the edge of the officer part

keywords          : "keywords"
wordcount         : "X"

@@

In our own experience, it is often not possible to convince all co-authors to switch to a different document processing environment, such as RMarkdown. That is, we have experienced that after writing up the first draft in Rmarkdown, one must eventually switch to a dynamically generated Word-file that is from then on used as static file that is used as basis for multiple iterations among the co-authors. This means, that ideally, one would have to manually merge the final Word file back to the RMarkdown souce, which generally is only possible manually. But we believe that even if this final step does not happen that - as long as dynamically generated elements are not manipulated - ensuring the reproducibility of the analysis and the initial draft is a big step forward. A less elegant but potentially more practical workflow may involve the officer package (@gohel2019officer). The officer package allows the manipulation of  Word (.docx) and PowerPoint (*.pptx) documents, that is, given a formatted template file, one can dynamically paste images, tables and text into documents from R.

>>>>

keywords          : "keywords"
wordcount         : "`r wordcountaddin::word_count(here::here('rr-flow.Rmd'))`"

@@

In our own experience, it is often not possible to convince all co-authors to switch to a different document processing environment, such as RMarkdown. That is, we have experienced that after writing up the first draft in Rmarkdown, one must eventually switch to a dynamically generated Word-file that is from then on used as static file that is used as basis for multiple iterations among the co-authors. This means, that ideally, one would have to manually merge the final Word file back to the RMarkdown souce, which generally is only possible manually. But we believe that even if this final step does not happen that - as long as dynamically generated elements are not manipulated - ensuring the reproducibility of the analysis and the initial draft is a big step forward. Making such static Word-file more dynamic is is possible with the officer package [@gohel2019officer], which allows the manipulation of  Word (.docx) and PowerPoint (.pptx) documents. That is, given a formatted static template file, one can dynamically paste images, tables and text into documents from R. We consider such static file with dynamic content, less elegant but potentially more practical, when not all authors can adhere to the described process.
